\begin{abstract}
Generative large language model (LLM) inference and parameter-efficient personalization increasingly rely on GPU acceleration, yet GPUs observe the full activation transcript: prompt-derived hidden states, key-value (KV) cache entries, LoRA adapter factors, and per-step gradients. End-to-end execution inside a trusted execution environment (TEE) is impractical at LLM scale, while pure GPU offload exposes precisely what we wish to protect.

We present an artifact-backed prototype of \emph{operator-compatible masked execution} for decoder-only LLM inference and LoRA personalization. A trusted-side controller---emulated locally in our prototype and \emph{not} a real TEE deployment---samples fresh masks per call, applies them on the \emph{right} of the activation tensor so that decoder-only generation, KV-cache append, rotary position embedding (RoPE)~\cite{su2021roformer}, and grouped-query attention (GQA)~\cite{ainslie2023gqa} remain compatible, and offloads dense matrix multiplication to an untrusted GPU. Nonlinear layers are surrounded by \emph{operator-compatible nonlinear islands}: paired channel permutations for GELU/ReLU and SwiGLU~\cite{shazeer2020glu}, orthogonal masks for RMSNorm~\cite{zhang2019rmsnorm}, and mean-preserving orthogonal masks for LayerNorm~\cite{ba2016layernorm}. The same machinery extends to a private LoRA training path---masked LoRA forward, masked LoRA backward, rank padding with five stronger dummy distributions, and a multi-layer training step. Loss and optimizer remain trusted-side; the adapter is never merged into the public base weight.

We evaluate the prototype with (i) empirical correctness equality versus a plain reference for GPT-2~\cite{radford2019language} and a modern decoder-only wrapper (RMSNorm + SwiGLU + RoPE + GQA), including prefill, decode-step, and greedy generation; (ii) adaptive proxy attackers---ridge and MLP inverters, signature- and Sinkhorn-based permutation recovery, membership-style linkability AUC, LoRA adapter and gradient extraction, spectral-cliff and ensemble rank inference, and a cost-model timing classifier; and (iii) a local-emulation wall-clock benchmark. Every claim in the paper is pinned to an audit row classified as \texttt{supported} (8 claims), \texttt{proxy\_supported} (5 claims), or \texttt{unsupported} (8 claims).

This is a prototype with proxy-evaluated security. We make no formal, cryptographic, or semantic-security claim; we do not report real TEE wall-time; we do not implement full Qwen/TinyLlama/LLaMA LoRA fine-tuning; we do not integrate PEFT~\cite{peft2022}, DeepSpeed~\cite{rasley2020deepspeed}, vLLM~\cite{kwon2023vllm}, or FlashAttention~\cite{dao2022flashattention}; we do not claim that the padded LoRA rank itself is hidden; loss and optimizer remain trusted-side. Within these explicit boundaries, our results show that generation-compatible right masking, operator-compatible nonlinear islands, and a private LoRA training path produce a transcript on which the strongest proxy attackers we evaluate are kept close to random chance, while the wrapper reproduces the plain reference output token-for-token in the tested configurations.
\end{abstract}
